\documentclass[../document]{subfiles}

\begin{document}

\newglossaryentry{JSON}
 {
   name=JSON,
   description={JSON, or JavaScript Object Notation, is an open standard format that uses simple text easily readable by humans to transmit objects consisting of attribute-value pairs. It is a language-independent data format.}
}

\newglossaryentry{NTNU}
{
   name=NTNU,
   description={Norwegian University of Science and Technology. Located in Trondheim, Norway.}
}

\newglossaryentry{SQL}
{
   name=SQL,
   description={Is a programming language designed for database management in a relational database management system.}
}

\newglossaryentry{Altran}
{
   name=Altran,
   description={Altran Technologies, SA is a global consulting firm founded in 1982 in France. It is an international group and a global leader in high technology and innovation consultancy.}
}

\newglossaryentry{API}
{
   name=API,
   description={API, or application programming interface, is a set of protocols for building software applications. An API typically dictates how specific components of a system should interact. In many cases they come in a library, and often significantly ease the time the programmer would otherwise need to put a piece of software together.}
}

\newglossaryentry{HTTP}
{
   name=HTTP,
   description={HTTP, or Hypertext Transfer Protocol, is an application protocol for hypermedia information systems. It is the foundation for communication on the Internet, or World Wide Web, and is widely used everywhere, with many versions being released over the years.}
}

\newglossaryentry{Java}
{
   name=Java,
   description={Java is a programming language. It is class-based and object oriented, and one of the most popular programming languages today. Java applications are compiled to run on any computer architecture, and as such Java is very popular on mobile devices as well.}
}

% only REST, not restful

\newglossaryentry{REST}
{
   name=REST,
   description={REST, or Representational state transfer is an abstract of the architecture of the World Wide Web. A RESTful application is used in web-services and network communication, and must follow the architectural constraints of REST.}
}

\newglossaryentry{Cloudant}
{
   name=Cloudant,
   description={Cloudant is an IBM owned product, delivered primarily as a cloud-based solution. It is an open-source, non-relational database service that requires no configuration. It is based on Apache-backed CouchDB.}
}

\newglossaryentry{Raspberry Pi}
{
   name=Raspberry Pi,
   description={Raspberry Pi, is a single-board computer, developed by the Raspberry Pi foundation to teach basic computer science. It comes in several variations, with different storage and connective capabilities. In our project it functions as a central hub, receiving sensor data from all the sensors attached to it.}
}

\newglossaryentry{JavaFX}
{
   name=JavaFX,
   description={JavaFX is a Java API. It is a set of Java packages specifically designed for graphics and media implementation. JavaFX 2.2 and later releases are fully integrated with Java SE Runtime Environment. This is the JavaFX version we use in our implementation.}
}

\newglossaryentry{DASH7}
{
   name=DASH7,
   description={DASH7 is an open source protocol for wireless sensor networking. The signal operates in 433MHz. The range of the signal can go all the way up to two kilometres with an accuracy of one meter, it has low latency for connecting with moving things. All these attributes makes it the perfect candidate for our sensors.}
}

\newglossaryentry{Android}
{
   name=Android,
   description={Android is a mobile operation system based on Linux made by Google. It is made with touch screen smart mobile devices in mind such as smartphones and tablets.}
}

\newglossaryentry{DHCP}
{
   name=DHCP,
   description={The Dynamic Host Configuration Protocol (DHCP) is a standardized network protocol used on Internet Protocol (IP) networks for dynamically distributing network configuration parameters, such as IP addresses for interfaces and services}
}


\end{document}
