\documentclass[../document.tex]{subfiles}

\begin{document}

\section{Project Plan}
In this chapter we will present our organisational plan, including the methodology that we use and how we plan to split the project in manageable phases. The list of risks accompanied by their mitigation plan, as well as quality assurance is included in the latter part of this chapter.

This chapter will help our team compare the initial plan of the project with the actual work that we have done after the twelve weeks have passed, allowing for good self-evaluation. Furthermore, we believe that a plan is necessary to maintain good pacing and finish the project on time.

\newpage
\subsection{Resources}
Here we will list the resources available for the team during the course of this project.

\subsubsection{Human resources}
The team consists of 7 members. Assisting us will be a teaching assistant, commonly referred to as the supervisor or adviser. Finally, the customer is also involved in the project and will be assisting us during the duration of the project with feedback and advice.

\subsubsection{Time Resources}
The project spans over twelve weeks. The weekly effort calculated per team member is roughly 24.5 hours, which is rounded up to 25 hours per member per week. Therefore the total amount of time that is to be spent on the project, as an upper estimate is: 12 weeks * 25 hours per week * 7 team members, which equals to 2100 working hours during the course of the project.
\newline \ \newline
The project will have to meet two important deadlines:
\begin{itemize}
\item
October 17th: A pre-delivery to the examiner needs to be handed in to the group supervisor and the external examiner. The pre-delivery consists of documentation that will familiarize the external examiner with our project.
\item
November 20th: Between 9:15 and 14:00 we will be holding the presentation of our project, which also includes a demonstration as well as the final hand-in to the supervisor and the present examiners. An electronic copy will also be handed in to the project coordinator a day before the final presentation.
\end{itemize}

\subsection{Project Organization}
In this section we will list our project organization. This includes a short interlude to our methodology and the key roles identified in the group.

\subsubsection{Methodology - Scrum}
The team will be organized using the Agile methodology. To be more precise, we are going to use Scrum. More details about why we chose Scrum and the normal procedures used in an agile environment can be found in the preliminary study chapter.

\subsubsection{Roles}
The team is going to have a list of roles defined in order to know the responsibilities assigned with the role. The team will only have a few permanent roles that were already assigned by the university but the rest of the roles will be taken by turn by every team member. 
\end{document}