\documentclass[../document]{subfiles}

\begin{document}

\section{Project Reflection}
\subsection{Introduction}
This chapter gives a reflection of how the project unfolded. The main focus of this reflection will be on how the work process went regarding how we worked together as a team, the relationship with the customer and the project task, the challenges we encountered during this process, and how the course could be made better. 

\subsection{Group Dynamics}
The groups for this project were assigned randomly with seven to eight group members in each group. Our group have seven group members, consisting of mixed genders and nationalities. As we have multiple nationalities within the group, English was the preferred language. Consequently, the entire project has been done in English. This section will look into how the group dynamic has been during this project, and what we would have done differently if we were to do the project again. 

\subsubsection{How the Project Went}
When we first met to start planning the project, the entire group agreed to try to work together as much as possible. We also agreed that we should have a fixed meeting schedule to avoid having to plan new meeting hours every week. During the project, these meeting times sometimes changed for several reasons, but we always started the meetings at the planned place and time unless something else was decided. Because one of our group members has a full time job, he was not able to be a part of the group meetings in parts of the project. To solve this we decided to have the planned meetings without him, and have contact with him when he had the time. We also decided that he should have his own tasks to solve. 

In the beginning of the project we used some time brainstorming ideas for the project, which was a good way to start the process. We got used to working together from the start, and everyone knew the plan for the project. As the project went on to a more concrete planning phase the tasks were easily distributed between the group members because everyone had been a part of creating the idea for the project. Everyone also took responsibility to finish their own tasks, and help those who needed help. 

When we started the sprints we split the tasks within the group based on what we initially wanted to work on. Furthermore, as we wanted everyone to learn as much as possible from this project, we intended to rotate the tasks on a regular basis. However, as the project proceeded and we made changes in the idea for both the prototype and the database, most of the group members continued working on the same types of tasks. This was done because it seemed to be the most efficient choice. Consequently, the only type of task that was done by all the group members was to write documentation. Even though we did not rotate the tasks, the group has handled changes in the project in a good way. Every time a change has been made the entire group has taken responsibility to finish the new tasks, and to make both the prototype and the documentation as good as possible.

\subsubsection{What We Would Have Done Differently}
The collaboration within the group has been good throughout the project, and we have therefore been able to make both a prototype and report that we are satisfied with. We have learned that working together, at the same time and in the same place, is a good idea. This is because we always had the opportunity to help each other when that was necessary. This made it easier to write documentation and to solve implementation issues. However, looking back at the project, there are several things we could have done differently. 

As a result of us not rotating the different tasks between the group members, we had to divide the documentation so that everyone could write about the parts they knew best. This was not a big problem, but it could have been avoided to some extent if everyone had the same understanding about the entire project. To make sure that everyone knew exactly what was going on in all the different parts of the system, we should have had regular meetings with the entire group. 

Because one of our group members had a full time job, we mostly had contact with him through another group member. However, this way of working did not give the group a good overview of what he had done, and what he was doing next. Also, he did not have a complete overview over what we were doing, or what decisions we had made. This led to both us and him working based on assumptions rather than facts, which again led to some misunderstandings. One way that these misunderstandings could have been avoided is by having meetings with the entire group, or at least several members of the group, including the one that had the full time job. In this way, the entire group could have the exact same information about the project. Another way to avoid this could have been to write an agenda for the meeting between the two group members, so that nothing was forgotten. Also, the group members in the meeting should write a summary of the meeting that everyone could read later. 

\subsection{The Work Process}
This section describes how the initial requirement process went, and how the subsequent scrum process went. 

\subsubsection{Requirements}
We started our work process with a requirement phase to plan the project, and document the requirements as accurately as possible before we started on the sprints. During this phase we used a lot more time than expected creating ideas and forming requirements that the customer was satisfied with. As a result the requirements phase was extended by a week compared with our project plan, which resulted in all the sprints being postponed by a working week.

\subsubsection{Scrum}
Even though we decided to use Scrum as our methodology during the preliminary study, we never actually followed the scrum methodology strictly. Before every sprint we made a sprint backlog with time estimations and priorities so that everyone would know what needed to be done during each sprint. The time estimations turned out to be a lot harder to gauge than expected. In the first sprint we underestimated the time needed to finish the tasks, and in sprint two and three we ended up overestimating the time needed in fear of underestimating again. As a result we have had more time available to work on documentation during sprint two and three than expected.

At the end of the sprint we wrote the sprint documentation and evaluated the sprint before planning the next sprint. Because we almost never did any work outside of the group meetings, we never had an actually scrum stand-up meeting to inform each other of our progress and plans forward. We all told each other what we were doing when we started working and when we changed tasks. We experienced that this way of working was efficient because we were all working together, and ended up skipping the planned weekly meetings. 

Furthermore, even though the requirements process was finished, we modified the requirements, test plan and architecture several times as the project tasks changed. The actual tasks for the next sprint was decided after the last sprint was finished and evaluated by the customer. As a result of this, it was easy to change our plans for the prototype as it became clearer to us what the customer wanted.

The main advantage we experienced related to working with scrum in this project was that the implementation phase was divided into sprints. Because we got feedback from the customer after every sprint, we also had the chance to change the path of the project when starting the next sprint.  

\subsection{Risk Management}
\label{risk_management}
Most of the risks predicted in the planning phase occurred one or several times during this project. This section will explain which risks that occurred and how we handled them.  The risks predicted in the planning phase can be found in the \subsubfullref{risks_and_risk_mitigation}

\subsubsection{Risk 2 - New Technologies}
During the course of the project this risk occurred frequently. This was predicted during risk analysis by assigning this risk a high probability. 

\paragraph{\gls{JavaFX}} \ \\
From the start it was apparent that the group would have to implement a graphical interface in \gls{Java}. After some initial investigation it was decided to use \gls{JavaFX}, a library of which the group had little previous knowledge. According to the risk strategy, three group members gained knowledge of \gls{JavaFX} by implementing a simple table view during the first sprint. The code itself and code comments served as documentation. 

\paragraph{NoSQL Database} \ \\
At the customer meeting September 26, it was requested that the group replace their \gls{SQL} database with a more suitable NoSQL solution. The group needed to investigate possible solutions from scratch, a demanding task that was assigned to two group members with a technical understanding. During the course of a week, they explored a considerable number of technologies involved in different solutions, documenting their usage with well-commented code snippets. The effort eventually resulted in a commented prototype implementation of the database that served as a final reference on technology usage.

\paragraph{Maven Project Management} \ \\
The customer also requested that the group use Maven for project management. One of the group members attended to a Skype conversation with the customer where Maven project management was addressed briefly. In addition, the two group members working on the replacement database solution integrated the project in Maven on a separate code branch. This setup was later integrated into the rest of the project. The POM files (Project Object Model) served as documentation for Maven project management. Some other group members were briefed in Maven, enough to understand the POM files. It was not deemed necessary that all group members know Maven.

\paragraph{Latex} \ \\
The group decided early to write their report in Latex. One group member with considerable Latex experience wrote a brief introduction to Latex, with links to further reading.

\paragraph{The vdvil Project} \ \\
According to customer requests, the group needed to investigate the vdvil project, a previous project the customer had been involved in. One group member attended to a Skype conversation with the customer, and wrote a short note on how to set up the project for the other group members.

% Technology risks that occurred that were not mentioned:
% Git, GitHub. IntelliJ IDEA.
% \gls{Raspberry Pi} central hub and sensors. Central hub Network setup

\subsubsection{Risk 3 - Use External Services}
To keep track of our documentation and code we used a combination of Google Drive and GitHub. Even though these services never went down, we handled this risk by having a back up on a personal machine run by one of the group members. 

\subsubsection{Risk 4 - Sickness}
Throughout the project several of the group members got sick on one point or another. As a result of this, we sometimes lacked group members on the different meetings. We handled this by redistributing the tasks needed to be done between the remaining group members before we started working. The person that was sick was responsible to inform the rest of the group as soon as possible. 

\subsubsection{Risk 5 - Absence Because of Other Schedules}
As all the group members have a full schedule, it was sometimes necessary for most of the group members to do something else than work on this project during the hours that we had scheduled to use on the project. To prevent this to have too much impact on the project the person missing was responsible to inform the rest of the group a soon as possible, and the tasks that were suppose to be done by the missing person were reassigned to other group members, if necessary. As one of our group members could not meet on most of the group meetings because of work, we assigned him with his own tasks and tried to communicate as much as possible with him to avoid misunderstandings. 

\subsubsection{Risk 7 - Miscommunication}
During the project we had some miscommunication both between the group and the customer, and between group members. The miscommunication often took some time to discover, which sometimes led to unnecessary work being done. However, when a miscommunication was discovered we handled it by discussing within the group why the miscommunication occurred, what it was about, and what we wanted to do next. Then we would present the plan further with the other party involved in the miscommunication. We would also ask relevant questions to the other party to get answers about the parts that were misunderstood, if there was any misunderstanding. 

\subsection{Time Estimation}

We estimated that the whole project would take 2150 hours to complete, in the end we calculated that we had used 2005 hours on this project. A detailed overview of the time can be found in this subsection, both in textual format and as a table in \tableref{tab:time_estimate}


The planning of this project changed a few times throughout the duration of the project. Therefore the estimated hours are different than the hours we actually spent on the given tasks. The self-learning in the start took much more time than we expected, as we needed to connect as a group and attend lectures, in addition to brainstorming ideas for the prototype. However, during the rest of the project we spent around fifteen hours on self-study, which was what we estimated. The hours spent on planning the project in the beginning took somewhat time than we had estimated. 

Writing the requirements specification had some factors that changed the work load. At first we spent more hours than estimated on the requirements because the project needed many more requirements than we first thought. However, due to big changes in our system, we needed to discuss the changes instead of writing requirements. This led to that we worked less than half of what was estimated the third week. The fourth week we worked on the requirements for sixty hours. These hours were not included in the estimated work hours, but they were needed, to rewrite the requirements for the smart room into requirements for the visualiser.

We had planned to start sprint 1 in the fourth week, so the time estimated for the first week of sprint 1 was entirely wrong. During the next three sprints we worked less on the documentation and the implementation than estimated. This is because there were many changes done by the customer during the sprints. Some of the time we had planned to work on the sprints were used to discuss and to figure out how to solve the changes the customer wanted. We also needed to learn new frameworks for the database twice, which took time. Another factor that made the time we estimated wrong, was the absence of one group member. That group member worked outside the scheduled meeting times, and focused his efforts mostly on the \gls{Raspberry Pi} and the sensors. In the latter weeks, we added a sprint we did not plan to have. While a few members wrote the documentation as we had planned, the rest worked on the last changes in the visualiser. Therefore we spent less time on the finalization of the report than we had estimated. 

We did not estimate the time all the meetings during this project took, which was usually one hour of meeting followed by one or more hours of discussion. Overall we had many changes during the project, so we did not follow the estimated hours quite as planned. The overview of estimated hours, per each activity and week of work can be seen in \tableref{tab:time_estimate}.


\begin{table}
\caption{Overview of Estimated Hours}
\centering
\label{tab:time_estimate}
\begin{tabularx}{\textwidth}{|l|X|X|L{1.6cm}|L{1cm}|}
	\hline
	\textbf{Task}
	&\textbf{From week}
	&\textbf{To week}
	&\textbf{Estimated hours}
	&\textbf{Actual hours}
	\\ \hline \textbf{Misc}
	&
	&
	&
	&
	\\ \hline Self study
	&1
	&13
	&195
	&282.5
	\\ \hline Planning
	&1
	&2
	&165
	&116.5
	\\ \hline Initial requirements specification
	&2
	&4
	&190
	&157.5
	\\ \hline \textbf{Sprint 1}
	&
	&
	&
	&
	\\ \hline Sprint 1 implementation
	&4
	&6
	&117
	&157
	\\ \hline Sprint 1 documentation
	&4
	&6
	&120
	&46
	\\ \hline \textbf{Sprint 2}
	&
	&
	&
	&
	\\ \hline Sprint 2 implementation
	&7
	&8
	&187
	&116
	\\ \hline Sprint 2 documentation
	&7
	&8
	&120
	&41
	\\ \hline \textbf{Pre-delivery for the examiner}
	&
	&
	&
	&
	\\ \hline Pre-Delivery for the examiner
	&7
	&8
	&30
	&21.5
	\\ \hline \textbf{Sprint 3}
	&
	&
	&
	&
	\\ \hline Sprint 3 implementation
	&9
	&10
	&124
	&77.5
	\\ \hline Sprint 3 documentation
	&9
	&10
	&120
	&130.5
	\\ \hline \textbf{Sprint 4}
	&
	&
	&
	&
	\\ \hline Sprint 4 implementation
	&11
	&13
	&60
	&34
	\\ \hline Sprint 4 documentation
	&11
	&13
	&40
	&41
	\\ \hline \textbf{Presentation and documentation}
	&
	&
	&
	&
	\\ \hline Review and finalize project
	&11
	&13
	&320
	&330.5
	\\ \hline Prepare Presentation
	&13
	&13
	&40
	&48
	\\ \hline \textbf{Meetings}
	&
	&
	&
	&
	\\ \hline Group meeting
	&1
	&13
	&182
	&258
	\\ \hline Adviser meeting
	&1
	&13
	&78
	&78
	\\ \hline Customer meeting
	&1
	&13
	&78
	&69.5
	\\ \hline 
\end{tabularx}
\end{table}

\subsection{Quality Assurance}
In the planning phase of this project we defined some quality metrics that measure how well our prototype is implemented, and how we plan to ensure that these quality metrics are met in our prototype. This section will describe which parts of the plan worked and which that did not, along with what we ended up doing instead of the plan.

To ensure high quality of the documentation and the code we planned on using online shared repositories. This was done through the entire project and it ensured that everyone had an overview of the documentation and the code at all times. Furthermore, to ensure that the code is easy to understand, even for those not familiar with the code, we planned on using already defined coding standards for \gls{Java}. This included writing JavaDocs for all the classes and additional comments where that was needed. After the comments were written, the entire group could more easily get an overview of what the other group members had done. To make working with GitHub easier we planned on following some guidelines described in the quality assurance section.

To ensure high quality in our communication with the customer, and in our work in general, we planned on having weekly meetings with both the customer and the adviser. While the adviser meetings have been held on a regular basis, the customer meetings has been more sporadic. The reason is that we never found a fixed time to have the customer meetings, and ended up having to schedule meetings at different hours every week. As a result of this, some misunderstandings occurred and some meetings were cancelled, leading to irregular contact with the customer.

\subsection{The Customer and the Project Task}
During this project a considerable amount of miscommunication occurred between the group and the customer. More than once the group efforts were misdirected. An example is that we first thought we were going to do something with the sensors, like creating a smart room. However, this was more than the customer asked for, as he only wanted a visualiser for the data. Despite the miscommunication between us and the customer, the relation we had with him was generally good throughout the entire project. The communication issues taught us a lot about how to communicate with a customer, which will come in handy later in life. One of the most important lessons we learned was that we should have had a fixed meeting schedule with the customer. With a fixed meeting schedule we would have been able to avoid some misunderstandings about the meeting time, and we would therefore been able to have meetings more frequently than what we had during this project. With more meetings we could have avoided having to make changes to parts of the prototype that we had worked a lot on because it was not quite right. Another lesson was that we should be more specific from the start when talking to the customer. No information about the project should be unsaid so that there are no misunderstandings about what we plan to do and what we have done.   

The customer was located in Oslo, therefore all the meetings we had with him were over Skype. The only other way we interacted with the customer was by mail, and we had maximum one meeting per week. Therefore, when we started to work on a sprint it often took a week before we could get feedback. This lead to us having to change the visualiser or the database more than once. 

During this project, one of the suggestions made by the customer, and one of the biggest lessons we have learned about implementation, is to write the code as modifiable as possible. All the changes that have been made during the project would not have been as easy to carry out without modifiable code. Because of this we now know, after experience, that one should always try to make implementations as modifiable as possible in case of any future changes. 

\subsection{The Adviser}
The adviser has been a good resource for this project. He has both been giving us valuable feedback about the documentation, and advice about how we should communicate with the customer. The meetings we have had with him also taught us how valuable it is to have a regular meeting schedule, so that there are no misunderstandings, as well as an even flow of feedback. Furthermore, we have learned of the importance of a manager-like figure in a project like this.

\subsection{Suggestions for Improvement}
There are many good aspects of how this course is carried out. Each of the groups has the freedom to decide how to do the project. The adviser is there to guide the groups, which is helpful for knowing whether or not the project is on the right track. However, some aspects of the course could benefit from some change. The mandatory team building session came too late in the project. We had already been working together for a while and have gotten to know each other before the session. The session should be done with only a couple of groups at once. With a smaller group, we could have had a better discussion not only in the group, but also between the groups. Finally, the guest lecture about technical writing in English could benefit from being one of the first guest lectures. The lecture was very well written and presented, and was quite helpful, but not many students showed up. Often, many students only attend the first few lectures, and then prioritise other work.

\subsection{Summary}
Over the duration of this project we have all gained a lot of new experiences. The group has been cooperating well, even if not everyone has been able to attend the group meetings. We have been able to collaborate on several tasks, help each other when that has been necessary, and handle challenges in a reflected manner. When we planned the project and the initial requirements, we pictured the development in the project in a quite different way than what actually happened. But because of our detailed risk management plan and initial project plan, dealing with any of the changes that occurred during the project went quite easy. All in all we are very pleased with what we have been able to achieve in this project.








\end{document}
